The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

  A few additional quantities are used to characterize the jets:
  the density contrast between the thermal gas contained in the jet source and the ambient gas,\
  $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
  the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
  the pressure ratio of CR to gas is 0.18,\
  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
  along the symmetric axis of cylinder.\
  The jet power is thus $3.2\times 10^{42}$ erg/s, resulting in the Eddington ratio 0.008.

  Note that as we inject the jets at the center of the clumpy disc,\
  we define the ambient gas density by the peak density of\
  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

>>>>

  A few additional quantities are used to characterize the jets:
  the density contrast between the thermal gas contained in the jet source and the atmosphere gas,\
  $\rho_{\text{jet}}/\rho_{\text{amb}}=10^{-3}$,\
  the temperature contrast, $T_{\text{jet}}/T_{\text{amb}}=2\times10^{4}$,\
  the pressure ratio of CR to gas is 0.18,\
  and the flow 4-velocity inside the jet source $\beta\gamma = 0.6$\
  along the symmetric axis of cylinder.\
  The jet power is thus $3.2\times 10^{42}$ erg/s, resulting in the Eddington ratio 0.008.

  Note that as we inject the jets at the center of the clumpy disc,\
  we define the atmosphere gas density by the peak density of\
  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.
